---
title: "Covid19 Spread"
author: "HG"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    css: style.css
    vertical_layout: scroll
runtime: shiny
---
    

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
source("global.R")
library(DT)
```

<style>                     
  .navbar {
    background-color:black;
    border-color:black;
  }
.navbar-brand {
  color:white!important;
}
</style> 


Sidebar {.sidebar}
=======================================================================

```{r}
 selectInput("country", label = h3("Country (unique)"), 
    choices = countries, 
    selected = "France")
```

```{r}
 selectInput("countries", label = h3("Countries (multiple)"), 
    choices = countries, 
    selected = c("France","Germany",'China','US','Spain','Italy'),multiple=T)
```


World
=======================================================================

Row {data-height=100}
-----------------------------------------------------------------------

### Global {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = "World",
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Day {.value-box}

```{r}
renderValueBox({
  valueBox(
    value =latest_day,
    icon = "fa-calendar",
    color= "#222226",
  )
})
```

### Total number of confirmed cases {.value-box}

```{r}
renderValueBox({
  numcases<- world_data %>% dplyr::filter(date==latest_day)
  numcases<- numcases$nb_conf_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-line-chart",
    color= "#222226",
  )
})
```

### Total number of death cases {.value-box}

```{r}
renderValueBox({
  numcases<- world_data %>% dplyr::filter(date==latest_day)
  numcases<- numcases$nb_death_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Total number of recovered cases {.value-box}

```{r}
renderValueBox({
  numcases<- world_data %>% dplyr::filter(date==latest_day)
  numcases<- numcases$nb_recov_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

Row {data-height=100}
-----------------------------------------------------------------------

### Total active cases {.value-box}

```{r}
renderValueBox({
  numcases<- world_data %>% dplyr::filter(date==latest_day)
  numcases<- numcases$nb_active_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Mortality {.value-box}

```{r}
renderValueBox({
  numcases<- world_data %>% dplyr::filter(date==latest_day)
  numcases<- round((numcases$nb_death_cases[1]/numcases$nb_conf_cases[1])*100,2) 
  valueBox(
    value =paste(numcases,"%",sep = " "),
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### New cases (today) {.value-box}

```{r}
renderValueBox({
  confcases<- world_data %>% dplyr::filter(date==latest_day)
  valueBox(
    value =confcases$nb_conf_day_cases[1],
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```


### Death cases (today) {.value-box}

```{r}
renderValueBox({
  deathcases<- world_data %>% dplyr::filter(date==latest_day)
  valueBox(
    value =deathcases$nb_death_day_cases[1],
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Recovered cases (today) {.value-box}

```{r}
renderValueBox({
  recovcases<- world_data %>% dplyr::filter(date==latest_day)
  valueBox(
    value =recovcases$nb_recov_day_cases[1],
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```


Row {data-height=500}
-----------------------------------------------------------------------
### Top countries 

```{r}
top_countries<- COV19_data %>% dplyr::filter(date==latest_day) %>% select(country,date,nb_conf_cases,nb_death_cases,nb_recov_cases,nb_active_cases)%>% mutate(mortality=round(nb_death_cases*100/nb_conf_cases,2)) %>% arrange(desc(nb_conf_cases))
renderDT({
  datatable(top_countries,colnames = c('Country'='country','Date'="date",'Nb. of confirmed cases'="nb_conf_cases","Nb. of death cases"='nb_death_cases','Nb. of recovered cases'='nb_recov_cases','Mortality'='mortality','Nb. of active cases'='nb_active_cases'))
})
```

Row {data-height=400, .tabset}
-----------------------------------------------------------------------

### Confirmed cases (Cumulated)
    
```{r}
renderPlotly({
    plot_conf<- world_data %>% ggplot(aes(date,nb_conf_cases))+
  geom_line() + labs(x="Date",y="Number of confirmed cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot_conf,tooltip = c("date","nb_conf_cases")))
})
```

### Confirmed cases (Daily)
    
```{r}
renderPlotly({
    plot_conf<- world_data %>%
  ggplot(aes(date,nb_conf_day_cases))+
  geom_col() + labs(x="Date",y="Number of daily confirmed cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot_conf,tooltip = c("date","nb_conf_day_cases")))
})
```

Row {data-height=400, .tabset}
-----------------------------------------------------------------------

### Death cases (Cumulated)
    
```{r}
renderPlotly({
    plot<- world_data %>%  ggplot(aes(date,nb_death_cases))+
  geom_line() + labs(x="Date",y="Number of death cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_death_cases")))
})
```

### Death cases (Daily)
    
```{r}
renderPlotly({
    plot<- world_data %>%
  ggplot(aes(date,nb_death_day_cases))+
  geom_col() + labs(x="Date",y="Number of daily death cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_death_day_cases")))
})
```

Row {data-height=400, .tabset}
-----------------------------------------------------------------------

### Recovered cases (Cumulated)
    
```{r}
renderPlotly({
    plot<- world_data %>%  ggplot(aes(date,nb_recov_cases))+
  geom_line() + labs(x="Date",y="Number of recovered cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_recov_cases")))
})
```

### Recovered cases (Daily)
    
```{r}
renderPlotly({
    plot<- world_data %>%
  ggplot(aes(date,nb_recov_day_cases))+
  geom_col() + labs(x="Date",y="Number of daily recovered cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_recov_day_cases")))
})
``` 


Row {data-height=400, .tabset}
-----------------------------------------------------------------------

### Active cases
    
```{r}
renderPlotly({
    plot<- world_data %>%  ggplot(aes(date,nb_active_cases))+
  geom_line() + labs(x="Date",y="Number of active cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_active_cases")))
})
```

Unique Country
=======================================================================

Row {data-height=100}
-----------------------------------------------------------------------

### Country {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = input$country,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Day {.value-box}

```{r}
renderValueBox({
  valueBox(
    value =latest_day,
    icon = "fa-calendar",
    color= "#222226",
  )
})
```

### Total number of confirmed cases {.value-box}

```{r}
renderValueBox({
  numcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  numcases<- numcases$nb_conf_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Total number of death cases {.value-box}

```{r}
renderValueBox({
  numcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  numcases<- numcases$nb_death_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Total number of recovered cases {.value-box}

```{r}
renderValueBox({
  numcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  numcases<- numcases$nb_recov_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

Row {data-height=100}
-----------------------------------------------------------------------

### Total active cases {.value-box}

```{r}
renderValueBox({
  numcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  numcases<- numcases$nb_conf_cases[1] - numcases$nb_death_cases[1]-numcases$nb_recov_cases[1]
  valueBox(
    value =numcases,
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Mortality {.value-box}

```{r}
renderValueBox({
  numcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  numcases<- round((numcases$nb_death_cases[1]/numcases$nb_conf_cases[1])*100,2) 
  valueBox(
    value =paste(numcases,"%",sep = " "),
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### New cases (today) {.value-box}

```{r}
renderValueBox({
  confcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  valueBox(
    value =confcases$nb_conf_day_cases[1],
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```


### Death cases (today) {.value-box}

```{r}
renderValueBox({
  deathcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  valueBox(
    value =deathcases$nb_death_day_cases[1],
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```

### Recovered cases (today) {.value-box}

```{r}
renderValueBox({
  recovcases<- COV19_data %>% dplyr::filter(country==input$country & date==latest_day)
  valueBox(
    value =recovcases$nb_recov_day_cases[1],
    icon = "fa-area-chart",
    color= "#222226",
  )
})
```


Row {data-height=400}
-----------------------------------------------------------------------

### Confirmed cases (Cumulated)
    
```{r}
renderPlotly({
    plot_conf<- COV19_data %>% dplyr::filter(country==input$country) %>%
  ggplot(aes(date,nb_conf_cases))+
  geom_line() + labs(x="Date",y="Number of confirmed cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot_conf,tooltip = c("date","nb_conf_cases")))
})
```

### Confirmed cases (Daily)
    
```{r}
renderPlotly({
    plot_conf<- COV19_data %>% dplyr::filter(country==input$country) %>%
  ggplot(aes(date,nb_conf_day_cases))+
  geom_col() + labs(x="Date",y="Number of daily confirmed cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot_conf,tooltip = c("date","nb_conf_day_cases")))
})
```

Row {data-height=400}
-----------------------------------------------------------------------

### Death cases (Cumulated)
    
```{r}
renderPlotly({
    plot<- COV19_data %>% dplyr::filter(country==input$country) %>%
  ggplot(aes(date,nb_death_cases))+
  geom_line() + labs(x="Date",y="Number of death cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_death_cases")))
})
```

### Death cases (Daily)
    
```{r}
renderPlotly({
    plot<- COV19_data %>% dplyr::filter(country==input$country) %>%
  ggplot(aes(date,nb_death_day_cases))+
  geom_col() + labs(x="Date",y="Number of daily death cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_death_day_cases")))
})
```

Row {data-height=400}
-----------------------------------------------------------------------

### Recovered cases (Cumulated)
    
```{r}
renderPlotly({
    plot<- COV19_data %>% dplyr::filter(country==input$country) %>%
  ggplot(aes(date,nb_recov_cases))+
  geom_line() + labs(x="Date",y="Number of recovered cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_recov_cases")))
})
```

### Recovered cases (Daily)
    
```{r}
renderPlotly({
    plot<- COV19_data %>% dplyr::filter(country==input$country) %>%
  ggplot(aes(date,nb_recov_day_cases))+
  geom_col() + labs(x="Date",y="Number of daily recovered cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_recov_day_cases")))
})
``` 

Row {data-height=400}
-----------------------------------------------------------------------

### Active cases
    
```{r}
renderPlotly({
    plot<- COV19_data %>% dplyr::filter(country==input$country) %>%
  ggplot(aes(date,nb_active_cases))+
  geom_line() + labs(x="Date",y="Number of active cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
    print(ggplotly(plot,tooltip = c("date","nb_active_cases")))
})
```

Multiple Countries
=======================================================================
Row {data-height=500}
-----------------------------------------------------------------------
### Top countries 

```{r}

renderDT({
  top_countries<- COV19_data %>% dplyr::filter(country %in% input$countries & date==latest_day) %>% select(country,date,nb_conf_cases,nb_death_cases,nb_recov_cases, nb_active_cases)%>% mutate(mortality=round(nb_death_cases*100/nb_conf_cases,2))
  datatable(top_countries,colnames = c('Country'='country','Date'="date",'Nb. of confirmed cases'="nb_conf_cases","Nb. of death cases"='nb_death_cases','Nb. of recovered cases'='nb_recov_cases','Mortality'='mortality','Nb. of active cases'='nb_active_cases'))
})
```

Row {data-height=400}
-----------------------------------------------------------------------

### Total number of confirmed cases
    
```{r}
renderPlotly(
  plot_conf<- COV19_data %>% dplyr::filter(country %in% input$countries) %>%
  ggplot(aes(date,nb_conf_cases,color=country))+
  geom_line() + labs(x="Date",y="Number of confirmed cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
)
```

Row {data-height=400}
-----------------------------------------------------------------------

### Total number of death cases
    
```{r}
renderPlotly(
  plot_conf<- COV19_data %>% dplyr::filter(country %in% input$countries) %>%
  ggplot(aes(date,nb_death_cases,color=country))+
  geom_line() + labs(x="Date",y="Number of death cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
)
```
   
Row {data-height=400}
-----------------------------------------------------------------------

### Total number of recovered cases
    
```{r}
renderPlotly(
  plot_conf<- COV19_data %>% dplyr::filter(country %in% input$countries) %>%
  ggplot(aes(date,nb_recov_cases,color=country))+
  geom_line() + labs(x="Date",y="Number of recovered cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
)
```


Row {data-height=400}
-----------------------------------------------------------------------

### Total number of active cases
    
```{r}
renderPlotly(
  plot_conf<- COV19_data %>% dplyr::filter(country %in% input$countries) %>%
  ggplot(aes(date,nb_active_cases,color=country))+
  geom_line() + labs(x="Date",y="Number of active cases",caption = "Source: Johns Hopkins \n Coronavirus Center") +
  dark_theme_gray()+ scale_color_brewer("Countries",palette = 'Dark2')
)
```
